Inpainting with controlled frequency suppression in the Fourier domain

### 2011-06-24 project/Paper/paper.tex
Entered values of final submission

\begin{table*}
\begin{center}
\begin{tabular}{|l|p{6cm}|r|r|}
\hline
Parameter & Description & Initial value & Optimized value\\
\hline
gauss\_size & Size of the Gaussian kernel in pixels & 10 & ? \\
gauss\_sigma & Sigma of the Gaussian kernel & 1 & ? \\
patch\_size & Patch size as exponent to the basis 2 & 4 & ? \\
patch\_frame\_size & Frame size in pixels & 8 & ? \\
td\_abortbelow\_stdev & Minimal standard deviation while evaluating thresholds as negative exponent to basis 10& 3 & ? \\
td\_abortbelow\_stepsize & Minimal step size while evaluating thresholds as negative exponent to basis 10& 4 & ? \\
td\_middle & Initial threshold & 10 & ? \\
validation & Fraction of pixels in the validation set & 0.4 & ? \\
max\_iterations & Maximum number of iterations & 5 & ? \\
abortbelow\_change & Minimal relative change to perform another iteration & 0.1 & ? \\
\hline
\end{tabular}
\end{center}
\caption{Parameters with their initial and optimized values.}
\label{parameters}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{|l|p{6cm}|r|r|}
\hline
Parameter & Description & Initial value & Optimized value\\
\hline
gauss\_size & Size of the Gaussian kernel in pixels & 10 & 19 \\
gauss\_sigma & Sigma of the Gaussian kernel & 1 & 0.6523 \\
patch\_size & Patch size as exponent to the basis 2 & 4 & 9 \\
patch\_frame\_size & Frame size in pixels & 8 & 0 \\
td\_abortbelow\_stdev & Minimal standard deviation while evaluating thresholds as negative exponent to basis 10& 3 & 1.9395 \\
td\_abortbelow\_stepsize & Minimal step size while evaluating thresholds as negative exponent to basis 10& 4 & 3.5226 \\
td\_middle & Initial threshold & 10 & 16.1555 \\
validation & Fraction of pixels in the validation set & 0.4 & 0.0151 \\
max\_iterations & Maximum number of iterations & 5 & 7 \\
abortbelow\_change & Minimal relative change to perform another iteration & 0.1 & 0.0465 \\
\hline
\end{tabular}
\end{center}
\caption{Parameters with their initial and optimized values. Optimized values are rounded, if necessary (e.g. to whole pixels)}
\label{parameters}
\end{table*}
